### 2016-08-30 version0.0/paper1.tex
Applying Sarah's comments on ch2.

%P5: How to measure it
A galaxy's metallicity is another physical quantity that likely plays a role in the rate of star formation. However, it affects each component of star formation laws in a different way, making it complicated to fully understand its implications. There are many studies on correlation of metallicity with stellar mass and SFR, as well as the effect of metallicity on the ISM \citep[e.g.][]{Boissier03, Leroy08, Krumholz09, Mannucci10, Dib11a, Dib11b, Lilly13}. These studies suggest that metallicity has a critical role in the formation of H$_2$ gas. Thus there should be a correlation between metallicity and the SFR. \citet{Krumholz09} introduced a theoretical SFR law which suggests that the SFR and metallicity of galaxies have a power-law correlation, but the power-law index changes with the amount of total gas. 
 Using results obtained from both observations and analytical models, \citet{Mannucci10} and \citet{Lilly13} showed that metallicity depends on both stellar mass and the SFR, which they referred to as a 'fundamental metallicity relation'. They found that at any fixed stellar mass, metallicity and the SFR have an inverse correlation. It should be noted that the above two correlations are only valid in the global case. However, \citet{Leroy08} showed that the SFR as measured by combining far-UV and 24~$\mu$m emission does not change with changing metallicity. \citet{Roychowdhury15} argued that in nearby spiral galaxies effect of metallicity on the SFR calculation is smaller than the calibration errors and can be ignored. On the other side, \citet{Boissier03} showed that metallicity has an inverse correlation with CO-H$_2$ conversion factor. Therefore, using a constant conversion factor at high metallicity regions causes the overestimation of the molecular gas mass, and in low metallicity it leads to an underestimation.

@@

%P6(2*): What we did and why Andromeda
In this paper, we present our results from testing and comparing both the K-S law and the Extended Schmidt law on the Andromeda galaxy (M31). Additionally, we applied these two laws on three different regions in M31 to determine whether there is any dependence on distance from the centre of the galaxy. Since M31 is the nearest spiral galaxy to our own, high resolution images of this galaxy are available, providing data from various regions with different physical properties (e.g. metallicity, surface brightness, gas density). This inside look helps us test star formation laws in diverse physical conditions. Thus M31 is a suitable testbed for studying scaling laws.

@@

To calculate the mass of H$_2$ from the molecular hydrogen column density, we estimated the volume and volume density of H$_2$ in each pixel. Then, using M$_{H_2} = \mu_{H_2}m_H\rho_{H_2}$ where $ \mu_{H_2}$ is the mean molecular mass of H$_2$, m$_H$ is the mass of one hydrogen atom and $\rho_{H_2}$ is the volume density, we calculated M$_{H_2}$.

>>>>

%P5: How to measure it
A galaxy's metallicity is another physical quantity that likely plays a role in the rate of star formation. However, it affects each component of star formation laws in a different way, making it complicated to fully understand its implications. There are many studies of correlations of metallicity with stellar mass and SFR, as well as the effect of metallicity on the ISM \citep[e.g.][]{Boissier03, Leroy08, Krumholz09, Mannucci10, Dib11a, Dib11b, Lilly13}. These studies suggest that metallicity has a critical role in the formation of H$_2$ gas. Thus there should be a correlation between metallicity and the SFR. \citet{Krumholz09} introduced a theoretical SFR law which suggests that the SFR and metallicity of galaxies have a power-law correlation, but the power-law index changes with the amount of total gas. 
 Using results obtained from both observations and analytical models, \citet{Mannucci10} and \citet{Lilly13} showed that metallicity depends on both stellar mass and the SFR, which they referred to as a `fundamental metallicity relation'. They found that at any fixed stellar mass, metallicity and the SFR have an inverse correlation. It should be noted that the above two correlations are only valid in the global case. However, \citet{Leroy08} showed that the SFR as measured by combining far-UV and 24~$\mu$m emission does not change with changing metallicity. \citet{Roychowdhury15} argued that in nearby spiral galaxies effect of metallicity on the SFR calculation is smaller than the calibration errors and can be ignored. On the other side, \citet{Boissier03} showed that metallicity has an inverse correlation with CO-H$_2$ conversion factor. Therefore, using a constant conversion factor at high metallicity regions causes the overestimation of the molecular gas mass, and in low metallicity it leads to an underestimation.

@@

%P6(2*): What we did and why Andromeda
In this chapter, we present our results from testing and comparing both the K-S law and the Extended Schmidt law on the Andromeda galaxy (M31). Additionally, we applied these two laws on three different regions in M31 to determine whether there is any dependence on distance from the centre of the galaxy. Since M31 is the nearest spiral galaxy to our own, high resolution images of this galaxy are available, providing data from various regions with different physical properties (e.g. metallicity, surface brightness, gas density). This inside look helps us test star formation laws in diverse physical conditions. Thus M31 is a suitable testbed for studying scaling laws.

@@

To calculate the mass of H$_2$ from the molecular hydrogen column density, we estimated the volume and volume density of H$_2$ in each pixel. Then, using M$_{H_2} = \mu_{H_2}m_H\rho_{H_2}V$ where $ \mu_{H_2}$ is the mean molecular mass of H$_2$, m$_H$ is the mass of one hydrogen atom, $\rho_{H_2}$ is the volume density and $V$ is the volume of each pixel, we calculated M$_{H_2}$.
